External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising

### 2016-10-20 egpaper_for_review.tex
a

\section{The Denoising Algorithm}
\subsection{Adaptive Sparse Coding}
We employ the $\mathbf{U}$ as the adaptive dictioanry to represent the structural variations of the PGs in that component.
\begin{equation}\label{equ5}
\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{U}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{3p^{2}}\lambda_{i}|\boldsymbol{\upalpha}_{i}|.
\end{equation}
The $i$th entry of the regularization parameter $\lambda_{i}$ 
\begin{equation}\label{equ6}
\lambda_{i} = \lambda/(\mathbf{S}_{i}+\varepsilon),
\end{equation}
where $\varepsilon$ is a small positive number to avoid dividing by zero. Since the dictionary $\mathbf{U}$ is orthonormal, it is not difficult to find out that (\ref{equ4}) has a closed-form solution (detailed derivation can be found in the supplementary material):
\begin{equation}\label{equ7}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{4pt}
\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{U^{T}\overline{y}}_{m})\odot \text{max}(|\mathbf{U^{T}\overline{y}}_{m}|-\mathbf{\Lambda},\mathbf{0}),
\end{equation}
where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{U^{T}\overline{y}}_{m}|$ is the absolute value of each entry of vector $|\mathbf{U^{T}\overline{y}}_{m}|$. The closed-form solution makes our weighted sparse coding process very efficient.

@@

\begin{table}
\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Guided Internal Subspace Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, PG-GMM model
\\
1. Initialization: $\hat{\mathbf{x}}^{(0)}=\mathbf{y},\mathbf{y}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $t = 1:IteNum$ \textbf{do}
\\
2. Iterative Regularization:
\\
\quad\quad\quad $\mathbf{y}^{(t)}=\hat{\mathbf{x}}^{(t-1)}+\delta(\mathbf{y}-\mathbf{y}^{(t-1)})$;
\\
3. Estimate the standard deviation of noise;
\\
\quad\textbf{for} each PG $\mathbf{Y}$ \textbf{do}
\\
4.\quad Calculate group mean $\boldsymbol{\upmu}_{y}$ and form PG $\mathbf{\overline{Y}}$;
\\
5.\quad Gaussian component selection via (\ref{equ3});
\\
\quad\textbf{end for}
\\
\quad\textbf{for} each Internal Subspace \textbf{do}
\\
6.\quad Internal Subspace Learning by (\ref{equ4});
\\
7.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
\\
\quad\textbf{end for}
\\
8. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(t)}$;
\\
\textbf{end for}
\\
\textbf{Output:} The recovered image $\hat{\mathbf{x}}^{(IteNum)}$.\\
\hline
\end{tabular}
\end{table}

@@

The PSNR and SSIM resluts are listed in Table \ref{tab1}. The number in red color and blue color means the best and second best results, respectively. From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods. The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB. The 
\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided}  &\textbf{Guided2} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.68} & \color{red}{ 38.89}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9676} & \color{red}{0.9704}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}\label{tab2}
\caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided2} 
\\
\hline
\multirow{3}{*}{\small{Canon 5D Mark III}} 
& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & \color{blue}{38.76} & 38.37 & \color{red}{40.44}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 3200}   
& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & \color{blue}{35.69} & 35.37 & \color{red}{37.16}
\\ 
\cline{2-11}    
& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & \color{blue}{35.54} & 34.91 & \color{red}{37.06}  
\\
\hline
\multirow{3}{*}{Nikon D600} 
& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \color{red}{35.57} & 34.98 & \color{blue}{35.28}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 3200}   
& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \color{red}{36.70} & 35.95 & \color{blue}{36.62}
\\ 
\cline{2-11}    
& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & \color{blue}{40.51} & 38.68 & 39.28 & \color{red}{41.15} & 39.05
\\
\hline
\multirow{3}{*}{Nikon D800} 
& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & \color{blue}{38.01} & 37.99 & \color{red}{38.67}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 1600}   
& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \color{blue}{40.36} & \color{red}{40.81}
\\ 
\cline{2-11}    
& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & \color{blue}{38.30} & \color{red}{38.77}
\\
\hline
\multirow{3}{*}{Nikon D800} 
& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \color{red}{39.01} & \color{blue}{38.57}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 3200}   
& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \color{blue}{36.75} & \color{red}{36.82}
\\ 
\cline{2-11}    
& 32.91 & 32.98 & 32.96 & 38.54 & \color{blue}{40.05} & \color{red}{40.59} & 36.91 & 36.76 & 39.06 & 38.68
\\
\hline
\multirow{3}{*}{Nikon D800} 
& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & \color{blue}{34.25} & 31.28 & 33.49 & \color{red}{34.61} & 33.48
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 6400}   
& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \color{blue}{33.21} & \color{red}{33.29}
\\ 
\cline{2-11}    
& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & \color{blue}{33.22} & \color{red}{33.48}
\\
\hline
Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & \color{blue}{36.88} & \color{red}{ 37.21}
\\
\hline
Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & \color{blue}{0.9481} & \color{red}{ 0.9506}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\section{The Denoising Algorithm}
\subsection{Adaptive Sparse Coding}
To remove the real noise, we employ the sparse coding framework. And in order to be adaptive to the input image, we employ the internal learned $\mathbf{U}$ of each cluster as an adaptive dictioanry to represent the structural variations of the PGs in that cluster. The \emph{mutual incoherence} $\mu(\mathbf{U})$ \cite{donoho2003optimally}, which is difined as
\begin{equation}
\mu(\mathbf{U})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}
\end{equation},
is a measure of quality of dictionary. Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.

\begin{equation}\label{equ5}
\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{U}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{3p^{2}}\lambda_{i}|\boldsymbol{\upalpha}_{i}|.
\end{equation}
The $i$th entry of the regularization parameter $\lambda_{i}$ 
\begin{equation}\label{equ6}
\lambda_{i} = \lambda/(\mathbf{S}_{i}+\varepsilon),
\end{equation}
where $\varepsilon$ is a small positive number to avoid dividing by zero. Since the dictionary $\mathbf{U}$ is orthonormal, it is not difficult to find out that (\ref{equ4}) has a closed-form solution (detailed derivation can be found in the supplementary material):
\begin{equation}\label{equ7}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{4pt}
\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{U^{T}\overline{y}}_{m})\odot \text{max}(|\mathbf{U^{T}\overline{y}}_{m}|-\mathbf{\Lambda},\mathbf{0}),
\end{equation}
where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{U^{T}\overline{y}}_{m}|$ is the absolute value of each entry of vector $|\mathbf{U^{T}\overline{y}}_{m}|$. The closed-form solution makes our weighted sparse coding process very efficient.

@@

\begin{table}
\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Guided Internal Subspace Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, PG-GMM model
\\
1. Initialization: $\hat{\mathbf{x}}^{(0)}=\mathbf{y},\mathbf{y}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $t = 1:IteNum$ \textbf{do}
\\
\quad\textbf{for} each PG $\mathbf{Y}$ \textbf{do}
\\
2.\quad Calculate group mean $\boldsymbol{\upmu}_{y}$ and form PG $\mathbf{\overline{Y}}$;
\\
3.\quad Gaussian component selection via (\ref{equ3});
\\
\quad\textbf{end for}
\\
\quad\textbf{for} each Internal Subspace \textbf{do}
\\
4.\quad Internal Subspace Learning by (\ref{equ4});
\\
5.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(t)}$;
\\
\textbf{end for}
\\
\textbf{Output:} The recovered image $\hat{\mathbf{x}}^{(IteNum)}$.\\
\hline
\end{tabular}
\end{table}

@@

The PSNR and SSIM resluts are listed in Table \ref{tab1}. The number in red color and blue color means the best and second best results, respectively. From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods. The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB. The 
\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided}  &\textbf{Guided2} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.72} & \color{red}{ 38.90}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9694} & \color{red}{0.9702}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}\label{tab2}
\caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided2} 
\\
\hline
\multirow{3}{*}{\small{Canon 5D Mark III}} 
& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & \color{blue}{38.76} & 38.37 & \color{red}{40.50}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 3200}   
& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & \color{blue}{35.69} & 35.37 & \color{red}{37.22}
\\ 
\cline{2-11}    
& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & \color{blue}{35.54} & 34.91 & \color{red}{37.13}  
\\
\hline
\multirow{3}{*}{Nikon D600} 
& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \color{red}{35.57} & 34.98 & \color{blue}{35.34}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 3200}   
& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \color{red}{36.70} & 35.95 & \color{blue}{36.69}
\\ 
\cline{2-11}    
& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & \color{blue}{40.51} & 38.68 & 39.28 & \color{red}{41.15} & 39.17
\\
\hline
\multirow{3}{*}{Nikon D800} 
& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & \color{blue}{38.01} & 37.99 & \color{red}{38.82}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 1600}   
& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \color{blue}{40.36} & \color{red}{40.98}
\\ 
\cline{2-11}    
& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & \color{blue}{38.30} & \color{red}{38.90}
\\
\hline
\multirow{3}{*}{Nikon D800} 
& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \color{red}{39.01} & \color{blue}{38.69}
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 3200}   
& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \color{blue}{36.75} & \color{red}{36.82}
\\ 
\cline{2-11}    
& 32.91 & 32.98 & 32.96 & 38.54 & \color{blue}{40.05} & \color{red}{40.59} & 36.91 & 36.76 & 39.06 & 38.80
\\
\hline
\multirow{3}{*}{Nikon D800} 
& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & \color{blue}{34.25} & 31.28 & 33.49 & \color{red}{34.61} & 33.31
\\ 
\cline{2-11} 
\multirow{3}{*}{ISO = 6400}   
& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \color{red}{33.21} & \color{blue}{33.18}
\\ 
\cline{2-11}    
& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & \color{blue}{33.22} & \color{red}{33.35}
\\
\hline
Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & \color{blue}{36.88} & \color{red}{ 37.26}
\\
\hline
Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & \color{blue}{0.9481} & \color{red}{ 0.9505}
\\
\hline
\end{tabular}
\end{center}
\end{table*}
